Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements

### 2024-07-28 Submission.Rmd
coffee shop edits (Methods)

---
title             : "Subjective Experience of Demands and Resources across O*NET Job Elements"
shorttitle        : "O*NET JD-R"

@@

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance – it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]]. Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions [see Figure \@ref(fig:ourmodel)]:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows [see Figure \@ref(fig:ourmodel)]:

@@

@@

The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

O\*Net collects information about these categories by periodically asking workers job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*. We retained O\*Net’s response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems.

Data were collected through Prolific, an online data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18 or older and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the online survey after reading an informed consent. Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*). Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.

>>>>

---
title             : "Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements"
shorttitle        : "O*NET JD-R"

@@

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance – it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]. Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions (see Figure \@ref(fig:ourmodel)):

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \@ref(fig:ourmodel)):

@@

Data were collected through Prolific, an online data collection platform. An email was sent to **a random subset???** of all "eligible" members of the Prolific respondent pool, notifying them of their opportunity to participate. Eligibility requirements **included??** being 18 or older and holding either a full-time or part-time job. Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of **98???** different O\*Net job characteristics. For example, if a respondent indicated that any one characteristic **was not** applicable for their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

@@

The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding]. The O\*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

O\*Net collects information about these categories by periodically asking workers job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*. We retained O\*Net’s response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems. The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
